%//////////////////////////////////////////////////////////////////////////////
%
% Copyright (c) 2007,2009 Daniel Adler <dadler@uni-goettingen.de>, 
%                         Tassilo Philipp <tphilipp@potion-studios.com>
%
% Permission to use, copy, modify, and distribute this software for any
% purpose with or without fee is hereby granted, provided that the above
% copyright notice and this permission notice appear in all copies.
%
% THE SOFTWARE IS PROVIDED "AS IS" AND THE AUTHOR DISCLAIMS ALL WARRANTIES
% WITH REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED WARRANTIES OF
% MERCHANTABILITY AND FITNESS. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR
% ANY SPECIAL, DIRECT, INDIRECT, OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES
% WHATSOEVER RESULTING FROM LOSS OF USE, DATA OR PROFITS, WHETHER IN AN
% ACTION OF CONTRACT, NEGLIGENCE OR OTHER TORTIOUS ACTION, ARISING OUT OF
% OR IN CONNECTION WITH THE USE OR PERFORMANCE OF THIS SOFTWARE.
%
%//////////////////////////////////////////////////////////////////////////////

\newpage
\section{Motivation}

Interoperability between programming languages is a desirable feature 
in complex software systems. While functions in scripting languages and virtual machine
languages can be called in a dynamic manner, statically compiled programming
languages such as C, C++ and Objective-C lack this ability.\\
The majority of systems use C function interfaces as their system-level 
interface. Calling these (foreign) functions from within a dynamic environment 
often involves the development of so called "glue code" on both sides,
the use of external tools generating communication code, or integration
of other middleware fulfilling that purpose. However, even inside a completely
static environment, without having to bridge multiple languages, it
can be very useful to call functions dynamically. Consider, for example, message 
systems, dynamic function call dispatch mechanisms, without even knowing about the 
target.\\

The \product{dyncall} library project provides a clean and portable C interface
to dynamically issue calls to foreign code using small call kernels written in
assembly. Instead of providing code for every bridged function call, which
unnecessarily results in code bloat, only a modest number of instructions are used
to invoke all the calls.\\

\subsection{Static function calls in C}

The C programming language and its direct derivatives are limited in the way 
function calls are handled. A C compiler regards a function call as a
fully qualified atomic operation. In such a statically typed environment, this 
includes the function call's argument arity and type, as well as the
return type.\\


\subsection{Anatomy of machine-level calls}

The process of calling a function on the machine level yields a common pattern:

\begin{enumerate}
\item The target function's calling convention dictates how the stack is 
prepared, arguments are passed, results are returned and how to clean up
afterwards.
\item Function call arguments are loaded in registers and on the stack according
to the calling convention that take alignment constraints into account.
\item Control flow transfer from caller to callee.
\item Process return value, if any. Some calling conventions specify that
the caller is responsible for cleaning up the argument stack.
\end{enumerate}


\newpage

%\paragraph{Example}
The following example depicts a C source and the corresponding assembly for the X86 32-bit processor architecture.


\begin{lstlisting}[label=cfuncall,caption=C function call,language=C]
extern void f(int x, double y,float z);
void caller()
{
  f(1,2.0,3.0f);
}
\end{lstlisting}


\begin{lstlisting}[label=x86asm,caption=Assembly X86 32-bit function call,language={[x86masm]Assembler}]
.global f         ; external symbol 'f'
caller:
  push  40400000H ; 3.0f (32 bit float)
                  ; 2.0  (64 bit float)
  push  40000000H ;          low  DWORD
  push  0H        ;          high DWORD 
  push  1H        ; 1    (32 bit integer)
  call  f         ; call 'f'
  add   esp, 16   ; cleanup stack
\end{lstlisting}


\begin{comment}

Due to the statically compiled nature of the
language itself, the abstraction to the underlying hardware machine 
These languages make an abstraction to the machine in a way, where a function 
call is an atomic operation that has to be fully qualified at compilation time.

This library follows the approach to abstract the construction of a function call
and provides a small and clean implementation that is extendable by ports to
compilers, operating-systems and processor architectures.
The library solely uses a small kernel function to perform the actual call and
does not require just-in-time code generation.

General-purpose programming languages such as C\footnote{and derived programming
languages such as C++ and Objective-C} are powerful statically compiled 
programming languages that allow to implement low-level tasks. They abstract
the underlying hardware to a degree where one is allowed to write functions
that implement algorithms. At the same time, this

Although C is very powerful and a portable language to implement time-critical
and performance greedy application - it is limited in the way it handles calls
to functions.

General-purpose programming languages such as C and C++ are limited in the way 
function calls are handled. These languages make an abstraction to the 
underlying hardware architecture, so that writing algorithms can be done in a 
portable way. While C is quite flexible in case of pointer arithmetics and
I/O in main memory, the flexibility ends at the function call.

In contrast to implementing algorithms, the function call in C is something 
that is black-box to the language. 

One can either fully bind and call a function at once or none at all.

 construct a half-baked function-call without providing C code that performs a particular desired function call
in regard to arity, argument type list, return type and calling convention.
The compiler requires exact information about the desired calling convention, 
arity, argument- and return types.
\end{comment}

